Results visualization across sites

### 2021-11-30 metanalysis_visualization/visualization.Rmd
qc codes adapted for one more site

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis")
paket(listOfPackages)
```

@@

```{r}
outputDir <- "../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
```

@@

### Summary of the codes used per site 
```{r}
library(tidyr)

@@

# extract all codes that are available across all sites
codes_in_all_sites <- summary_codes[ complete.cases( summary_codes ), ]
codes_in_all_sites <- codes_in_all_sites[
  with(codes_in_all_sites, order(BCH, FRBDX, Lurie, UMICH, decreasing = TRUE)),
]
print( paste0("There are in total ", nrow( codes_in_all_sites), " codes in common across all sites"))

#### upSetR 
library(devtools)
install_github("jokergoo/ComplexHeatmap")
library( ComplexHeatmap)
BCH_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "BCH", "concept_code"]
FRBDX_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "FRBDX", "concept_code"]
Lurie_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "Lurie", "concept_code"]
UMICH_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "UMICH", "concept_code"]

concepts = list( 
          BCH = BCH_concepts$concept_code,
          FRBDX = FRBDX_concepts$concept_code, 
          Lurie = Lurie_concepts$concept_code, 
          UMICH = UMICH_concepts$concept_code
          )

@@

all_other_sites <- unique( c( FRBDX_concepts$concept_code, Lurie$concept_code, UMICH$concept_code ))
concepts_in_bch_not_in_other_sites <- BCH_concepts[! BCH_concepts$concept_code %in% all_other_sites, ]
codesToReview <- mental_codes_qc_output_all[ mental_codes_qc_output_all$concept_code %in% concepts_in_bch_not_in_other_sites$concept_code, ]

>>>>

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR")
paket(listOfPackages)

install_github("jokergoo/ComplexHeatmap")
library( ComplexHeatmap)
```

@@

```{r}
outputDir <- "../../output/latest_output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
country_map <- read.delim( file = paste0( outputDir, "country_mapping.txt"))
```

@@

### Summary of the codes used per site 
```{r}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) )

@@

# extract all codes that are available across all sites
codes_in_all_sites <- summary_codes[ complete.cases( summary_codes ), ]
codes_in_all_sites <- codes_in_all_sites[
  with(codes_in_all_sites, order(BCH, FRBDX, Lurie, UMICH, APHP, decreasing = TRUE)),
]
print( paste0("There are in total ", nrow( codes_in_all_sites), " codes in common across all sites"))

#### upSetR

BCH_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "BCH", "concept_code"]
FRBDX_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "FRBDX", "concept_code"]
Lurie_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "Lurie", "concept_code"]
UMICH_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "UMICH", "concept_code"]
APHP_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "APHP", "concept_code"]

concepts = list( 
          BCH = BCH_concepts$concept_code,
          FRBDX = FRBDX_concepts$concept_code, 
          Lurie = Lurie_concepts$concept_code, 
          UMICH = UMICH_concepts$concept_code, 
          APHP  = APHP_concepts$concept_code
          )

@@

all_other_sites <- unique( c( FRBDX_concepts$concept_code, APHP_concepts$concept_code,
                              Lurie_concepts$concept_code, UMICH_concepts$concept_code ))
concepts_in_bch_not_in_other_sites <- BCH_concepts[! BCH_concepts$concept_code %in% all_other_sites, ]
codesToReview <- mental_codes_qc_output_all[ mental_codes_qc_output_all$concept_code %in% concepts_in_bch_not_in_other_sites$concept_code, ]
